---
title: "20191120 Univariate Hypothesis Tests"
author: "Hanqian Zhang"
date: "2019/11/20"
output: html_document
---


## Setup


### Load Packages

```{r load-packages}
library(ggplot2)
library(dplyr)
library(statsr)
library(gmodels)
library(psych)
library(irr)
library(DescTools)
```

### Load Data


```{r dataimport}
preprocessed2018 = read.csv("/Users/tylerzhang/Desktop/CFPS Research-20191101T212903Z-001/dispatchedworkersCFPS/data/preprocessed2018.csv")
```


### Continuous Variables


Check if the continuous variable is different across DE and RE significantly with `ANOVA`


Test the strength of such association with `intra-class correlation`.


Null Hypothesis: The means of continuous variable for DE and RE are the same. 


#### ANOVA Results


| Num | var | label | F value | p value |
| :-- | :--:| :---: | :-----: | ------: |
| 1   | age               | 年龄                     | 0.039 |  0.842 |
| 2   | qg12              | 工作总收入               | 29.53 | 5.83e-08 *** |
| 3   | qg1001            | 月度公积金数额           | 33.53 | 7.55e-09 *** |
| 4   | qg901             | 个人每月缴纳多少钱的保险 | 18.86 | 1.44e-05 *** |
| 5   | qg702             | 过去一年的福利金额       | 2.08  |  0.149 |
| 6   | qg401             | 工作收入满意度           | 0.667 | 0.414 |
| 7   | qg406             | 工作总体满意度           | 0.712 | 0.399 |
| 8   | qg15              | 过去12个月是否升迁       | 0.322 |  0.57 |
| 9   | qn10025           | 对政府官员信任程度       | 2.609 | 0.106 |
| 10  | qn6011            | 认为政府腐败问题有多严重 | 0.238 | 0.625 |
| 11  | qn6014            | 我国就业问题有多严重     | 2.34  | 0.126 |
| 12  | qn6018            | 我国社会保障问题有多严重 | 0.147 | 0.702|
| 13  | qu802             |互联网对您获取信息的重要性| 8.103 | 0.00444 ** |
| 14  | qu702             | 使用互联网工作的频率     | 11.27 | 0.000797 *** |
| 15  | w01               | 最高学历                 | 39.87 | 3.01e-10 ***|
| 16  | qn201             | 通过电视台了解政治       | 0.69  |  0.406 |
| 17  | qn202             | 通过网络了解政治         | 5.764 | 0.0164 * |



#### Intraclass Correlation Results

| Num | var | label | ICC value | 95% CI of ICC |
| :-- | :--:| :---: | :-----: | ------: |
| 1   | age               | 年龄                     | 0.001088946  | [-0.0006684184, 0.6906002] |
| 2   | qg12              | 工作总收入               | 0.01500468   | [0.002138099, 0.9432771] |
| 3   | qg1001            | 月度公积金数额           | 0.05798476   | [0.01122362, 0.9845628] |
| 4   | qg901             | 个人每月缴纳多少钱的保险 | 0.03378815	  | [0.006033954, 0.9734842] |
| 5   | qg702             | 过去一年的福利金额       | 0.004679272  |  [0.006033954,	0.9734842] |
| 6   | qg401             | 工作收入满意度           | 0.006341793  | [0.0004043133,	0.8836294] |
| 7   | qg406             | 工作总体满意度           | 0.003071539	| [-0.0002393089, 0.8083172] |
| 8   | qg15              | 过去12个月是否升迁       | 0.0000000000 |  [-0.0008769064, 0.5263395] |
| 9   | qn10025           | 对政府官员信任程度       | 4.811808e-10 | [-0.0008855657, 0.5287866] |
| 10  | qn6011            | 认为政府腐败问题有多严重 | 0.004317418  | [-2.282288e-05, 0.8470133] |
| 11  | qn6014            | 我国就业问题有多严重     | 0.004208596  | [-3.327471e-05, 0.8440032] |
| 12  | qn6018            | 我国社会保障问题有多严重 | 0.002219837	| [-0.0004048158, 0.7695461] |
| 13  | qu802             |互联网对您获取信息的重要性| 0.006408379	| [0.0003970454,	0.8849001] |
| 14  | qu702             | 使用互联网工作的频率     | 0.009059340  | [0.0009350596, 0.9124673] |
| 15  | w01               | 最高学历                 | 0.05614695   | [0.01081839,	0.9840456]|
| 16  | qn201             | 通过电视台了解政治       | 0.0001784571 | [-0.0008499844	0.5659573] |
| 17  | qn202             | 通过网络了解政治         | 0.008747656  | [0.0008684445, 0.9099582] |

#### age

```{r ageANOVA&ICC}
age.aov <- aov(age ~ dispatch.Dispatch, data = preprocessed2018)
summary(age.aov)

ageICCDE <- preprocessed2018[24] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
ageICCRE <- preprocessed2018[24] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
ageICC <- t(data.matrix(data.frame(ageICCDE, ageICCRE[1:906,])))
psych::ICC(ageICC, alpha = 0.05)
# because each of the two categories (dispatch.Dispatch == 0, dispatch.Dispatch == 1) there are multiple different ratings (age), we will use ICC2 to measure the Intraclass Correlation Coefficient
# ICC1: Each target is rated by a different judge and the judges are selected at random. 
# ICC2: A random sample of k judges rate each target.
# ICC3: A fixed set of k judges rate each target.
```


#### qg12工作总收入

```{r qg12ANOVA}
qg12.aov <- aov(qg12 ~ dispatch.Dispatch, data = preprocessed2018)
summary(qg12.aov)

qg12ICCDE <- preprocessed2018[25] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
qg12ICCRE <- preprocessed2018[25] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
qg12ICC <- t(data.matrix(data.frame(qg12ICCDE, qg12ICCRE[1:906,])))
psych::ICC(qg12ICC, alpha = 0.05) 
```


#### qg1001月度公积金数额

```{r qg1001ANOVA}
qg1001.aov <- aov(qg1001 ~ dispatch.Dispatch, data = preprocessed2018)
summary(qg1001.aov)

qg1001ICCDE <- preprocessed2018[26] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
qg1001ICCRE <- preprocessed2018[26] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
qg1001ICC <- t(data.matrix(data.frame(qg1001ICCDE, qg1001ICCRE[1:906,])))
psych::ICC(qg1001ICC, alpha = 0.05) 
```


#### qg901个人每月缴纳多少钱的保险

```{r qg901ANOVA}
qg901.aov <- aov(qg901 ~ dispatch.Dispatch, data = preprocessed2018)
summary(qg901.aov)

qg901ICCDE <- preprocessed2018[27] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
qg901ICCRE <- preprocessed2018[27] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
qg901ICC <- t(data.matrix(data.frame(qg901ICCDE, qg901ICCRE[1:906,])))
psych::ICC(qg901ICC, alpha = 0.05) 
```


#### qg702	过去一年的福利金额

```{r qg702ANOVA}
qg702.aov <- aov(qg702 ~ dispatch.Dispatch, data = preprocessed2018)
summary(qg702.aov)

qg702ICCDE <- preprocessed2018[28] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
qg702ICCRE <- preprocessed2018[28] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
qg702ICC <- t(data.matrix(data.frame(qg702ICCDE, qg702ICCRE[1:906,])))
psych::ICC(qg702ICC, alpha = 0.05) 
```


#### qg401	工作收入满意度

```{r qg401ANOVA}
qg401.aov <- aov(qg401 ~ dispatch.Dispatch, data = preprocessed2018)
summary(qg401.aov)

qg401ICCDE <- preprocessed2018[29] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
qg401ICCRE <- preprocessed2018[29] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
qg401ICC <- t(data.matrix(data.frame(qg401ICCDE, qg401ICCRE[1:906,])))
psych::ICC(qg401ICC, alpha = 0.05) 
```


#### qg406	工作总体满意度	

```{r qg406ANOVA}
qg406.aov <- aov(qg406 ~ dispatch.Dispatch, data = preprocessed2018)
summary(qg406.aov)

qg406ICCDE <- preprocessed2018[30] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
qg406ICCRE <- preprocessed2018[30] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
qg406ICC <- t(data.matrix(data.frame(qg406ICCDE, qg406ICCRE[1:906,])))
psych::ICC(qg406ICC, alpha = 0.05) 
```


#### qg15	过去12个月是否升迁

```{r qg15ANOVA}
qg15.aov <- aov(qg15 ~ dispatch.Dispatch, data = preprocessed2018)
summary(qg15.aov)

qg15ICCDE <- preprocessed2018[31] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
qg15ICCRE <- preprocessed2018[31] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
qg15ICC <- t(data.matrix(data.frame(qg15ICCDE, qg15ICCRE[1:906,])))
psych::ICC(qg15ICC, alpha = 0.05) 
```

#### qn10025	对政府官员信任程度

```{r qn10025ANOVA}
qn10025.aov <- aov(qn10025 ~ dispatch.Dispatch, data = preprocessed2018)
summary(qn10025.aov)

qn10025ICCDE <- preprocessed2018[32] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
qn10025ICCRE <- preprocessed2018[32] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
qn10025ICC <- t(data.matrix(data.frame(qn10025ICCDE, qn10025ICCRE[1:906,])))
psych::ICC(qn10025ICC, alpha = 0.05) 
```


#### qn6011	认为政府腐败问题有多严重

```{r qn6011ANOVA}
qn6011.aov <- aov(qn6011 ~ dispatch.Dispatch, data = preprocessed2018)
summary(qn6011.aov)

qn6011ICCDE <- preprocessed2018[33] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
qn6011ICCRE <- preprocessed2018[33] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
qn6011ICC <- t(data.matrix(data.frame(qn6011ICCDE, qn6011ICCRE[1:906,])))
psych::ICC(qn6011ICC, alpha = 0.05) 
```


#### qn6014	我国就业问题有多严重

```{r qn6014ANOVA}
qn6014.aov <- aov(qn6014 ~ dispatch.Dispatch, data = preprocessed2018)
summary(qn6014.aov)

qn6014ICCDE <- preprocessed2018[34] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
qn6014ICCRE <- preprocessed2018[34] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
qn6014ICC <- t(data.matrix(data.frame(qn6014ICCDE, qn6014ICCRE[1:906,])))
psych::ICC(qn6014ICC, alpha = 0.05) 
```


#### qn6018	我国社会保障问题有多严重

```{r qn6018ANOVA}
qn6018.aov <- aov(qn6018 ~ dispatch.Dispatch, data = preprocessed2018)
summary(qn6018.aov)

qn6018ICCDE <- preprocessed2018[35] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
qn6018ICCRE <- preprocessed2018[35] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
qn6018ICC <- t(data.matrix(data.frame(qn6018ICCDE, qn6018ICCRE[1:906,])))
psych::ICC(qn6018ICC, alpha = 0.05) 
```


#### qu802	互联网对您获取信息的重要性

```{r qu802ANOVA}
qu802.aov <- aov(qu802 ~ dispatch.Dispatch, data = preprocessed2018)
summary(qu802.aov)

qu802ICCDE <- preprocessed2018[36] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
qu802ICCRE <- preprocessed2018[36] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
qu802ICC <- t(data.matrix(data.frame(qu802ICCDE, qu802ICCRE[1:906,])))
psych::ICC(qu802ICC, alpha = 0.05) 
```


#### qu702	使用互联网工作的频率

```{r qu702ANOVA}
qu702.aov <- aov(qu702 ~ dispatch.Dispatch, data = preprocessed2018)
summary(qu702.aov)

qu702ICCDE <- preprocessed2018[37] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
qu702ICCRE <- preprocessed2018[37] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
qu702ICC <- t(data.matrix(data.frame(qu702ICCDE, qu702ICCRE[1:906,])))
psych::ICC(qu702ICC, alpha = 0.05) 
```


#### w01	最高学历

```{r w01ANOVA}
w01.aov <- aov(w01 ~ dispatch.Dispatch, data = preprocessed2018)
summary(w01.aov)

w01ICCDE <- preprocessed2018[38] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
w01ICCRE <- preprocessed2018[38] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
w01ICC <- t(data.matrix(data.frame(w01ICCDE, w01ICCRE[1:906,])))
psych::ICC(w01ICC, alpha = 0.05) 
```


#### qn201	通过电视台了解政治

```{r qn201ANOVA}
qn201.aov <- aov(qn201_b_1 ~ dispatch.Dispatch, data = preprocessed2018)
summary(qn201.aov)

qn201ICCDE <- preprocessed2018[39] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
qn201ICCRE <- preprocessed2018[39] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
qn201ICC <- t(data.matrix(data.frame(qn201ICCDE, qn201ICCRE[1:906,])))
psych::ICC(qn201ICC, alpha = 0.05) 
```


#### qn202	通过电视台了解政治

```{r qn202ANOVA}
qn202.aov <- aov(qn202 ~ dispatch.Dispatch, data = preprocessed2018)
summary(qn202.aov)

qn202ICCDE <- preprocessed2018[40] %>%
  filter(preprocessed2018$dispatch.Dispatch == 1)
qn202ICCRE <- preprocessed2018[40] %>%
  filter(preprocessed2018$dispatch.Dispatch == 0)
qn202ICC <- t(data.matrix(data.frame(qn202ICCDE, qn202ICCRE[1:906,])))
psych::ICC(qn202ICC, alpha = 0.05) 
```




### Categorical Variables


Check if the categorical variables are significantly different across DE and RE with `chi-squared test`, test the strength of such association with `Cramer's V`


Null hypothesis: There is no significant difference between DE and RE


#### Results from Chi-Squared Tests and Cramer's V

| Num | var | label | chi-sq's p value | cramer's v |
| :--- | :---: | :-----: | :---: | ---: |
| 3   | gendermale        | 性别               | 0.07858 | 0.02798016 |
|     | genderfemale      | 性别 |             | | |
| 5   | qg10Yes           | 是否提供公积金     | 8.977e-05 | 0.06157909 |
|     | qg10No            | 是否提供公积金 |   | | |
| 6   | qn4003Yes         | 工会成员           | 0.0002616 | 0.05752974 |
|     | qn4003No          | 工会成员           |           |            |
| 7   | qea0未婚          | 当前婚姻状态       | 0.5423 | 0.02738961 |
| 8   | qea0在婚          | 当前婚姻状态       | | |
| 9   | qea0同居          | 当前婚姻状态       | | | 
| 10  | qea0离婚          | 当前婚姻状态       | | |
|     | qea0丧偶          | 当前婚姻状态       | dropped | |
| 11  | qp605公费治疗     | 您享有哪些医疗保险 | 0.001953 | 0.06780953 |
| 12  | qp605城镇居民     | 您享有哪些医疗保险 | | |
| 13  | qp605城镇治疗     | 您享有哪些医疗保险 | | |
| 14  | qp605补充医疗     | 您享有哪些医疗保险 | | |
| 15  | qp605新型农村     | 您享有哪些医疗保险 | | |
|     | qp605一无所有     | 您享有哪些医疗保险 | dropped | |
| 16  | qu201Yes          | 是否移动上网       | 0.001746 | 0.04955543 |
|     | qu201No           | 是否移动上网       | dropped |
| 17  | qu202Yes          | 是否电脑上网       | 2.774e-07 | 0.08059742 |
|     | qu202No           | 是否电脑上网       | dropped | |
| 18  | kwa2不喜爱学校    | 没升学的原因       | 0.002164 | 0.06372653|
| 19  | kwa2学业成绩      | 没升学的原因       | | |
| 20  | kwa2身体健康      | 没升学的原因       | | |
| 21  | kwa2经济困难      | 没升学的原因       | | |
|     | kwa2其他          | 没升学的原因       | dropped | |
| 22  | qn203Yes          | 过去12个月是否在网上发表过与政治问题和国家大事相关的言论 | 0.4692 | 0.01308001 |
|     | qn203No           | 过去12个月是否在网上发表过与政治问题和国家大事相关的言论 | dropped | |
| 23  | qn4001Yes         | 是否是党员         | 0.0206 | 0.03795618 |
|     | qn4001No          | 是否是党员         | dropped | |


#### gendermale 	性别（男）

```{r genderChiSq}
genderMatrix <- matrix(c(length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$gendermale == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$gendermale == 0)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$gendermale == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$gendermale == 0))),
                       ncol = 2, byrow = TRUE)
chisq.test(genderMatrix)
CramerV(genderMatrix)
```


#### qg10Yes 	是否提供公积金（是）

```{r qg10YesChiSq}
qg10YesMatrix <- matrix(c(length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qg10Yes == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qg10Yes == 0)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qg10Yes == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qg10Yes == 0))),
                       ncol = 2, byrow = TRUE)
chisq.test(qg10YesMatrix)
CramerV(qg10YesMatrix)
```


#### qn4003Yes 	工会成员（是）

```{r qn4003YesChiSq}
qn4003YesMatrix <- matrix(c(length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qn4003Yes == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qn4003Yes == 0)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qn4003Yes == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qn4003Yes == 0))),
                       ncol = 2, byrow = TRUE)
chisq.test(qn4003YesMatrix)
CramerV(qn4003YesMatrix)
```


#### qea0 	当前婚姻状态

```{r qea0ChiSq}
qea0Matrix <- matrix(c(length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qea0同居 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qea0在婚 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qea0未婚 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qea0离婚 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qea0离婚 == 0 & preprocessed2018$qea0同居 == 0 & preprocessed2018$qea0未婚 == 0 & preprocessed2018$qea0在婚 == 0)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qea0同居 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qea0在婚 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qea0未婚 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qea0离婚 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qea0离婚 == 0 & preprocessed2018$qea0同居 == 0 & preprocessed2018$qea0未婚 == 0 & preprocessed2018$qea0在婚 == 0))),
                       ncol = 2)
chisq.test(qea0Matrix)
CramerV(qea0Matrix)
```


#### qp605 	您享有哪些医疗保险

```{r qp605YesChiSq}
qp605Matrix <- matrix(c(length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qp605.公费治疗 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qp605.城镇居民 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qp605.城镇治疗 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qp605.新型农村 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qp605.补充医疗 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qp605.公费治疗 == 0 & preprocessed2018$qp605.城镇居民 == 0 & preprocessed2018$qp605.城镇治疗 == 0 & preprocessed2018$qp605.新型农村 == 0 & preprocessed2018$qp605.补充医疗 == 0)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qp605.公费治疗 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qp605.城镇居民 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qp605.城镇治疗 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qp605.新型农村 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qp605.补充医疗 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qp605.公费治疗 == 0 & preprocessed2018$qp605.城镇居民 == 0 & preprocessed2018$qp605.城镇治疗 == 0 & preprocessed2018$qp605.新型农村 == 0 & preprocessed2018$qp605.补充医疗 == 0))),
                       ncol = 2)
chisq.test(qp605Matrix)
CramerV(qp605Matrix)
```

#### qu201 	是否移动上网

```{r qu201YesChiSq}
qu201YesMatrix <- matrix(c(length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qu201Yes == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qu201Yes == 0)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qu201Yes == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qu201Yes == 0))),
                       ncol = 2, byrow = TRUE)
chisq.test(qu201YesMatrix)
CramerV(qu201YesMatrix)
```

#### qu202 	是否电脑上网

```{r qu202YesChiSq}
qu202YesMatrix <- matrix(c(length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qu202Yes == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qu202Yes == 0)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qu202Yes == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qu202Yes == 0))),
                       ncol = 2, byrow = TRUE)
chisq.test(qu202YesMatrix)
CramerV(qu202YesMatrix)
```


#### kwa2 	没升学的原因

```{r kwa2ChiSq}
kwa2Matrix <- matrix(c(length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$kwa2_b_1学业成绩 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$kwa2_b_1身体健康 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$kwa2_b_1经济困难 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$kwa2_b_1不喜欢学校 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$kwa2_b_1学业成绩 == 0 & preprocessed2018$kwa2_b_1身体健康 == 0 & preprocessed2018$kwa2_b_1经济困难 == 0 & preprocessed2018$kwa2_b_1不喜欢学校 == 0)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$kwa2_b_1学业成绩 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$kwa2_b_1身体健康 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$kwa2_b_1经济困难 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$kwa2_b_1不喜欢学校 == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$kwa2_b_1学业成绩 == 0 & preprocessed2018$kwa2_b_1身体健康 == 0 & preprocessed2018$kwa2_b_1经济困难 == 0 & preprocessed2018$kwa2_b_1不喜欢学校 == 0))),
                       ncol = 2)
chisq.test(kwa2Matrix)
CramerV(kwa2Matrix)
```


#### qn203 	过去12个月是否在网上发表过与政治问题和国家大事相关的言论

```{r qn203YesChiSq}
qn203YesMatrix <- matrix(c(length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qn203Yes == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qn203Yes == 0)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qn203Yes == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qn203Yes == 0))),
                       ncol = 2, byrow = TRUE)
chisq.test(qn203YesMatrix)
CramerV(qn203YesMatrix)
```


#### qn4001 	是否是党员

```{r qn4001YesChiSq}
qn4001YesMatrix <- matrix(c(length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qn4001Yes == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 1 & preprocessed2018$qn4001Yes == 0)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qn4001Yes == 1)),
                         length(which(preprocessed2018$dispatch.Dispatch == 0 & preprocessed2018$qn4001Yes == 0))),
                       ncol = 2, byrow = TRUE)
chisq.test(qn4001YesMatrix)
CramerV(qn4001YesMatrix)
```