---
title: "20191128 New Data Preprocessing"
output: html_document
---

## Setup


### Load Packages

```{r load-package}
library(ggplot2)
library(dplyr)
library(statsr)
library(gmodels)
```

### Load Data


```{r dataimport}
employment2018 = read.csv("/Users/tylerzhang/Desktop/CFPS Research-20191101T212903Z-001/dispatchedworkersCFPS/data/employment2018.csv")
```

| Num | var | label |
| :--- | :---: | -----: |
| 1   | pid      | 个人id |
| 2   | age      | 年龄 |
| 3   | gender   | 性别 |
| 4   | dispatch | 雇佣方法 |
| 5   | qg12     | 工作总收入 |
| 6   | qg10     | 是否提供公积金 |
| 7   | qg1001   | 月度公积金数额 |
| 8   | qg901    | 个人每月缴纳多少钱的保险 |
| 9   | qg702    | 过去一年的福利金额 |
| 10  | qn4003   | 工会成员 |
| 11  | qg401    | 工作收入满意度 |
| 12  | qg406    | 工作总体满意度 |
| 13  | qg15     | 过去12个月是否升迁 |
| 14  | qn10025  | 对政府官员信任程度 |
| 15  | qn6011   | 认为政府腐败问题有多严重 |
| 16  | qn6014   | 我国就业问题有多严重 |
| 17  | qn6018   | 我国社会保障问题有多严重 |
| 18  | qea0     | 当前婚姻状态 |
| 19  | qp605    | 您享有哪些医疗保险 |
| 20  | qu201    | 是否移动上网 |
| 21  | qu202    | 是否电脑上网 |
| 22  | qu802    | 互联网对您获取信息的重要性 |
| 23  | qu702    | 使用互联网工作的频率 |
| 24  | w01      | 最高学历 |
| 25  | kwa2     | 没升学的原因 |
| 26  | qn203    | 过去12个月是否在网上发表过与政治问题和国家大事相关的言论 |
| 27  | qn4001   | 是否是党员 |
| 28  | qn201    | 通过电视台了解政治 |
| 29  | qn202    | 通过网络了解政治 |


## Mapping Ordinal Variables

List of Ordinal Variables


| Num | var | label |
| :--- | :---: | -----: |
| 1  | qg401    | 工作收入满意度 |
| 2  | qg406    | 工作总体满意度 |
| 3  | qg15     | 过去12个月是否升迁 |
| 4  | qn10025  | 对政府官员信任程度 |
| 5  | qn6011   | 认为政府腐败问题有多严重 |
| 6  | qn6014   | 我国就业问题有多严重 |
| 7  | qn6018   | 我国社会保障问题有多严重 |
| 8  | qu802    | 互联网对您获取信息的重要性 |
| 9  | w01      | 最高学历 |


Except for w01 & qg15, all other ordinal variables have already been mapped to numbers in order.


```{r handling w01}
employment2018 <- employment2018 %>%
  mutate(w01 = ifelse(w01 == 10, 2, 
                      ifelse(w01 == 0, 1, w01))) %>%
  mutate(qg15 = ifelse(qg15 == 1 | qg15 == 2, 1,
                       ifelse(qg15 == 3, 2, 0)))
```


## One Hot Encoding for Nominal Variables

List of Nominal Variables 


| Num | var | label |
| :--- | :---: | -----: |
| 1   | gender   | 性别 |
| 2   | dispatch | 雇佣方法 |
| 3   | qg10     | 是否提供公积金 |
| 4   | qn4003   | 工会成员 |
| 5   | qea0     | 当前婚姻状态 |
| 6   | qp605    | 您享有哪些医疗保险 |
| 7   | qu201    | 是否移动上网 |
| 8   | qu202    | 是否电脑上网 |
| 9   | kwa2     | 没升学的原因 |
| 10  | qn203    | 过去12个月是否在网上发表过与政治问题和国家大事相关的言论 |
| 11  | qn4001   | 是否是党员 |

```{r nominalVarsPrep}
employment2018 <- employment2018 %>%
  mutate(gender = ifelse(gender == 1, "male", "female"))%>%
  mutate(qg10 = ifelse(qg10 == 5, "No", "Yes")) %>%
  mutate(qn4003 = ifelse(qn4003 == 5, "No", "Yes")) %>%
  mutate(qea0 = ifelse(qea0 == 1, "未婚",
                        ifelse(qea0 ==  2, "在婚",
                               ifelse(qea0 == 3,  "同居",
                                      ifelse(qea0 == 4, "离婚", "丧偶"))))) %>%
  mutate(qu201 = ifelse(qu201 == 5, "No", "Yes")) %>%
  mutate(qu202 = ifelse(qu202 == 5, "No", "Yes")) %>%
  mutate(kwa2_b_1 = ifelse(kwa2_b_1 == 1, "经济困难",
                           ifelse(kwa2_b_1 == 2, "学业成绩",
                                  ifelse(kwa2_b_1 == 3, "身体健康",
                                         ifelse(kwa2_b_1 ==  4, "不喜欢学校", "其他"))))) %>%
  mutate(qn203 = ifelse(qn203 == 5, "No", "Yes")) %>%
  mutate(qn4001 = ifelse(qn4001 == 5, "No", "Yes"))

employment2018 <- subset(employment2018, select = X:qn202)
```


```{r oneHot}
library(caret)

dmy <- dummyVars("~.", data = employment2018)
oneHot2018 <- data.frame(predict(dmy, newdata = employment2018))
```

```{r dropFirst}
oneHot2018 <- subset(oneHot2018, select = -c(genderfemale, dispatch.Contract, qg10No, qn4003No, qea0丧偶, qp605.一无所有, qu201No, qu202No, kwa2_b_1其他, qn203No, qn4001No))
```

## Standardization

```{r standardization}
library(psycho)

oneHot2018$pid <- factor(oneHot2018$pid)
oneHot2018$X <-factor(oneHot2018$X)
oneHot2018$gender <-factor(oneHot2018$gender)
oneHot2018$dispatch <-factor(oneHot2018$dispatch)
oneHot2018$qg10Yes <-factor(oneHot2018$qg10Yes)
oneHot2018$qn4003Yes <-factor(oneHot2018$qn4003Yes)
oneHot2018$qea0同居 <-factor(oneHot2018$qea0同居)
oneHot2018$qea0在婚 <-factor(oneHot2018$qea0在婚)
oneHot2018$qea0未婚 <-factor(oneHot2018$qea0未婚)
oneHot2018$qea0离婚 <-factor(oneHot2018$qea0离婚)
oneHot2018$qp605.公费治疗 <-factor(oneHot2018$qp605.公费治疗)
oneHot2018$qp605.城镇居民 <-factor(oneHot2018$qp605.城镇居民)
oneHot2018$qp605.城镇治疗 <-factor(oneHot2018$qp605.城镇治疗)
oneHot2018$qp605.新型农村 <-factor(oneHot2018$qp605.新型农村)
oneHot2018$qp605.补充医疗 <-factor(oneHot2018$qp605.补充医疗)
oneHot2018$qu201Yes <-factor(oneHot2018$qu201Yes)
oneHot2018$qu202Yes <-factor(oneHot2018$qu202Yes)
oneHot2018$kwa2_b_1不喜欢学校 <-factor(oneHot2018$kwa2_b_1不喜欢学校)
oneHot2018$kwa2_b_1学业成绩 <-factor(oneHot2018$kwa2_b_1学业成绩)
oneHot2018$kwa2_b_1经济困难 <-factor(oneHot2018$kwa2_b_1经济困难)
oneHot2018$kwa2_b_1身体健康 <-factor(oneHot2018$kwa2_b_1身体健康)

oneHot2018$qn203Yes <-factor(oneHot2018$qn203Yes)
oneHot2018$qn4001Yes <-factor(oneHot2018$qn4001Yes)
oneHot2018$qg401 <-factor(oneHot2018$qg401)
oneHot2018$qg406 <-factor(oneHot2018$qg406)
oneHot2018$qg15 <-factor(oneHot2018$qg15)
oneHot2018$qn10025 <-factor(oneHot2018$qn10025)
oneHot2018$qn6011 <-factor(oneHot2018$qn6011)
oneHot2018$qn6014 <-factor(oneHot2018$qn6014)
oneHot2018$qu802 <-factor(oneHot2018$qu802)
oneHot2018$qu702 <-factor(oneHot2018$qu702)
oneHot2018$w01 <-factor(oneHot2018$w01)
oneHot2018$qn201_b_1 <- as.numeric(oneHot2018$qn201_b_1)
oneHot2018$qn202 <- as.numeric(oneHot2018$qn202)


standardizedEmployment2018 <- oneHot2018 %>%
  psycho::standardize()
```


## Handling Null Variable/Impute

```{r knn Imputation}
library(VIM)

imputedEmployment2018 <- kNN(standardizedEmployment2018, variable = c("qg702", "qg12", "qg10Yes", "qg1001", "qg901", "qn4003Yes", "qg401", "qg15", "qn10025", "qn6011", "qn6014", "qn6018", "qea0同居", "qea0在婚", "qea0未婚", "qea0离婚", "qp605.公费治疗", "qp605.城镇居民", "qp605.城镇治疗", "qp605.新型农村", "qp605.补充医疗", "qu802", "qu702", "w01", "kwa2_b_1不喜欢学校", "kwa2_b_1学业成绩", "kwa2_b_1经济困难", "kwa2_b_1身体健康", "qn203Yes", "qn4001Yes", "qn201_b_1", "qn202"),  3)

imputedEmployment2018 <- subset(imputedEmployment2018, select = X:qn202)
```

### Destandardization 

```{r Destandardization}
imputedemployment2018 <- as.numeric(employment2018$qn201_b_1)

dsEmployment2018 <- imputedEmployment2018 %>%
  mutate(age = age * sd(employment2018$age, na.rm=TRUE)) %>%
  mutate(qg12 = qg12 * sd(employment2018$qg12, na.rm=TRUE)) %>%
  mutate(qg1001 = qg1001 * sd(employment2018$qg1001, na.rm=TRUE)) %>%
  mutate(qg901 = qg901 * sd(employment2018$qg901, na.rm=TRUE)) %>%
  mutate(qg702 = qg702 * sd(employment2018$qg702, na.rm=TRUE)) %>%
  mutate(qn201_b_1 = qn201_b_1 * sd(employment2018$qn201_b_1, na.rm=TRUE)) %>%
  mutate(qn202 = qn202 * sd(employment2018$qn202, na.rm=TRUE))

```




## The Updated List Variables

| Num | var | label | status |
| :--- | :---: | :-----: | ---: |
| 1   | pid               | 个人id | |
| 2   | age               | 年龄 | |
| 3   | gendermale        | 性别 | |
|     | genderfemale      | 性别 | dropped |
| 4   | dispatch.Dispatch | 雇佣方法 | |
|     | dispatch.Contract | 雇佣方法 | dropped |
| 5   | qg10Yes           | 是否提供公积金 | |
|     | qg10No            | 是否提供公积金 | dropped |
| 6   | qn4003Yes         | 工会成员 | |
|     | qn4003No          | 工会成员 | dropped | |
| 7   | qea0未婚          | 当前婚姻状态 | |
| 8   | qea0在婚          | 当前婚姻状态 | |
| 9   | qea0同居          | 当前婚姻状态 | |
| 10  | qea0离婚          | 当前婚姻状态 | |
|     | qea0丧偶          | 当前婚姻状态 | dropped |
| 11  | qp605公费治疗     | 您享有哪些医疗保险 | |
| 12  | qp605城镇居民     | 您享有哪些医疗保险 | |
| 13  | qp605城镇治疗     | 您享有哪些医疗保险 | |
| 14  | qp605补充医疗     | 您享有哪些医疗保险 | |
| 15  | qp605新型农村     | 您享有哪些医疗保险 | |
|     | qp605一无所有     | 您享有哪些医疗保险 | dropped |
| 16  | qu201Yes          | 是否移动上网 | |
|     | qu201No           | 是否移动上网 | dropped |
| 17  | qu202Yes          | 是否电脑上网 | |
|     | qu202No           | 是否电脑上网 | dropped |
| 18  | kwa2不喜爱学校    | 没升学的原因 | |
| 19  | kwa2学业成绩      | 没升学的原因 | |
| 20  | kwa2身体健康      | 没升学的原因 | |
| 21  | kwa2经济困难      | 没升学的原因 | |
|     | kwa2其他          | 没升学的原因 | dropped |
| 22  | qn203Yes          | 过去12个月是否在网上发表过与政治问题和国家大事相关的言论 | |
|     | qn203No           | 过去12个月是否在网上发表过与政治问题和国家大事相关的言论 | dropped |
| 23  | qn4001Yes         | 是否是党员 | |
|     | qn4001No          | 是否是党员 | dropped |
| 24 | qg12              | 工作总收入 | |
| 25  | qg1001            | 月度公积金数额 | |
| 26  | qg901             | 个人每月缴纳多少钱的保险 | |
| 27  | qg702             | 过去一年的福利金额 | |
| 28  | qg401             | 工作收入满意度 | |
| 29  | qg406             | 工作总体满意度 | |
| 30  | qg15              | 过去12个月是否升迁 | |
| 31  | qn10025           | 对政府官员信任程度 | |
| 32  | qn6011            | 认为政府腐败问题有多严重 | |
| 33  | qn6014            | 我国就业问题有多严重 | |
| 34  | qn6018            | 我国社会保障问题有多严重 | |
| 35  | qu802             | 互联网对您获取信息的重要性 | |
| 36  | qu702             | 使用互联网工作的频率 | |
| 37  | w01               | 最高学历 | |
| 38  | qn201             | 通过电视台了解政治 | |
| 39  | qn202             | 通过网络了解政治 | |


## Export Preprocessed Data

```{r exportData}
library(foreign)
write.dta(dsEmployment2018, "/Users/tylerzhang/Desktop/CFPS Research-20191101T212903Z-001/dispatchedworkersCFPS/data/newPreprocessed2018.dta")
write.csv(dsEmployment2018, "/Users/tylerzhang/Desktop/CFPS Research-20191101T212903Z-001/dispatchedworkersCFPS/data/newPreprocessed2018.csv")
```





